% =========================
% CV - based on the original homepage-style template
% =========================
\documentclass[a4paper,10pt]{article}

% ---------- Page ----------
\usepackage[a4paper,margin=0.85in]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% ---------- Fonts / Symbols ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{fontawesome5}

% ---------- Colors / Links ----------
\usepackage{xcolor}
\definecolor{accent}{HTML}{1F5FBF}
\definecolor{muted}{HTML}{444444}

\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=accent,
  citecolor=accent
}

% ---------- Layout helpers ----------
\usepackage{tabularx}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt, parsep=0pt}

% ---------- Section styling ----------
\usepackage{titlesec}
\titleformat{\section}
  {\Large\bfseries\color{accent}}
  {}{0pt}{}
  [\vspace{3pt}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\titleformat{\subsection}
  {\normalsize\bfseries\color{muted}}
  {}{0pt}{}
\titlespacing*{\subsection}{0pt}{6pt}{2pt}

% ---------- Small macros ----------
\newcommand{\sep}{\hspace{6pt}\textcolor{muted}{\textbar}\hspace{6pt}}
\newcommand{\entry}[4]{%
\textbf{#1}\hfill \textcolor{muted}{#2}\\
\textit{#3}\hfill \textcolor{muted}{#4}\\[-2pt]
}
\newcommand{\tinygap}{\vspace{3pt}}

% =========================
\begin{document}

% =========================
% Header
% =========================
\begin{tabularx}{\textwidth}{X r}
{\Huge \textbf{Minseong Cho}} &
\begin{minipage}[t]{0.43\textwidth}\raggedleft
\faEnvelope\ \href{mailto:mscho713@ajou.ac.kr}{mscho713@ajou.ac.kr}\\
\faPhone\ \href{tel:+821088037786}{+82 10-8803-7786}\\
\faGlobe\ \href{https://aloha713.github.io}{aloha713.github.io}\\
\faGraduationCap\ \href{https://scholar.google.com/citations?user=j9RODW0AAAAJ}{Google Scholar}\\
\textcolor{muted}{Suwon, South Korea}
\end{minipage}
\end{tabularx}

\vspace{6pt}
\textcolor{muted}{M.S. student in Mechanical Engineering, Ajou University \sep Active matter \sep Leidenfrost dynamics \sep Hair frizz dynamics}

% =========================
\section*{Summary}
Currently a graduate researcher at Ajou University. My research interests include active matter dynamics, the Leidenfrost effect, and hair frizz dynamics.

% =========================
\section*{Research Interests}
Active matter dynamics; Leidenfrost-induced motion; soft matter and fluid--structure interaction; hair frizz dynamics; centerline curvature and excursion analysis.

% =========================
\section*{Education}
\entry{Ajou University}{Sep 2025 -- Present}{M.S. in Mechanical Engineering}{Suwon, South Korea}
\textcolor{muted}{Advisor: Prof. Jonghyun Ha}\\
\tinygap
\entry{Ajou University}{Mar 2020 -- Aug 2025}{B.S. in Mechanical Engineering}{Suwon, South Korea}

% =========================
\section*{Research Experience}
\entry{Graduate Research Student, Softlab -- Ajou University}{Sep 2025 -- Present}{Hair frizz dynamics; boundary-driven active matter in soft hydrogels}{}
\begin{itemize}
  \item Study hair frizz dynamics using centerline-based geometric analysis and simulation-assisted interpretation.
  \item Analyze boundary-driven active matter in soft hydrogels, focusing on Leidenfrost-induced dynamics.
  \item Develop reproducible analysis and visualization scripts for experimental and simulation data.
  \item \textbf{Advisor:} Prof. Jonghyun Ha; Dr. Yeonsu Jung.
\end{itemize}

\entry{Undergraduate Research Student, Softlab -- Ajou University}{Mar 2023 -- Aug 2025}{Undergraduate research in soft matter and fluid mechanics}{}
\begin{itemize}
  \item Conducted research on Leidenfrost-related soft-matter dynamics.
  \item Performed image-based tracking, quantitative analysis, and figure preparation for presentations.
  \item \textbf{Advisor:} Prof. Jonghyun Ha; Dr. Yeonsu Jung.
\end{itemize}

% =========================
\section*{Selected Presentations}
\begin{itemize}
  \item \textbf{APS Division of Fluid Dynamics Meeting} (Houston, TX, USA; Nov 2025)\\
  \textit{Leidenfrost-induced active matter dynamics of spherical hydrogels}

  \item \textbf{Asian Congress of Fluid Mechanics} (Seoul, South Korea; Sep 2025)\\
  \textit{Leidenfrost-induced active matter dynamics of spherical hydrogels}

  \item \textbf{KSME Annual Conference} (Jeju, South Korea; Nov 2024)\\
  \textit{Explosive motion of spherical hydrogel via the Leidenfrost effect}
\end{itemize}

% =========================
\section*{Awards \& Honors}
\begin{itemize}
  \item \textbf{Dean's List} (Ajou University) \hfill \textcolor{muted}{Spring 2024, Spring 2025}\\
  Recognized for outstanding academic performance (top 5\% of the department).

  \item \textbf{Capstone Design Competition} (Ajou University) \hfill \textcolor{muted}{June 2025}\\
  2nd Place; KRW 1,000,000 prize. Project: compliant-mechanism-based knee assistive device for degenerative osteoarthritis prevention.

  \item \textbf{Gyeonggi-do Assistive Device Idea Competition} \hfill \textcolor{muted}{Nov 2025}\\
  3rd Place; KRW 300,000 prize. Project: compliant-mechanism-based knee assistive device for older adults.

  \item \textbf{APS DFD Travel/Enabling Grant} \hfill \textcolor{muted}{2025}\\
  US\$750 travel cost reimbursement for participation in the APS Division of Fluid Dynamics Meeting.
\end{itemize}

% =========================
\section*{Selected Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Programming} & Python, MATLAB, LaTeX \\
\textbf{Tools} & DeepLabCut, OpenCV, Git, Overleaf \\
\textbf{Methods} & image-based tracking, trajectory analysis, centerline extraction, curvature/excursion profiling, data visualization \\
\end{tabularx}

% =========================
\section*{References}
\textbf{Prof. Jonghyun Ha}\\
\textit{Assistant Professor, Department of Mechanical Engineering, Ajou University, Suwon, South Korea}\\
E-mail: \href{mailto:hajh@ajou.ac.kr}{hajh@ajou.ac.kr}\\
Scholar Profiles:
\href{https://www.softlab.ajou.ac.kr/people-ha}{Personal Page} \sep
\href{https://scholar.google.com/citations?user=H73RmsAAAAAJ}{Google Scholar}\\[5pt]

\textbf{Dr. Yeonsu Jung}\\
\textit{Postdoctoral Research Fellow, School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, USA}\\
E-mail: \href{mailto:jung@seas.harvard.edu}{jung@seas.harvard.edu}\\
Scholar Profiles:
\href{https://yeonsu-jung.github.io}{Personal Page} \sep
\href{https://scholar.google.com/citations?user=BMZc1CcAAAAJ}{Google Scholar}

\end{document}
