% =========================
% Academic CV - Minseong Cho
% =========================
\documentclass[a4paper,10pt]{article}

% ---------- Page ----------
\usepackage[a4paper,margin=0.82in]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}

% ---------- Fonts / Symbols ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{fontawesome5}

% ---------- Colors / Links ----------
\usepackage{xcolor}
\definecolor{accent}{HTML}{0B6B5D}
\definecolor{textmain}{HTML}{111111}
\definecolor{muted}{HTML}{555555}
\definecolor{rulegray}{HTML}{D7E2DF}

\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=accent,
  citecolor=accent
}

% ---------- Layout helpers ----------
\usepackage{tabularx}
\usepackage{enumitem}
\setlist[itemize,1]{
  label=\textbullet,
  leftmargin=1.15em,
  labelsep=0.55em,
  topsep=2pt,
  itemsep=4pt,
  parsep=0pt
}
\setlist[itemize,2]{
  label=\raisebox{0.15ex}{\scriptsize$\circ$},
  leftmargin=1.55em,
  labelsep=0.45em,
  topsep=1pt,
  itemsep=1pt,
  parsep=0pt
}

% ---------- Section styling ----------
\usepackage{titlesec}
\titleformat{\section}
  {\Large\bfseries\color{accent}}
  {}{0pt}{}
  [\vspace{3pt}{\color{rulegray}\titlerule}]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% ---------- Small macros ----------
\newcommand{\sep}{\hspace{6pt}\textcolor{muted}{\textbar}\hspace{6pt}}
\newcommand{\cvdate}[1]{\hfill \textcolor{textmain}{#1}}
\newcommand{\cvorg}[1]{\textcolor{muted}{#1}}
\newcommand{\cvaward}[1]{\textbf{#1}}
\newcommand{\cvfield}[2]{\textbf{#1:} #2}
\newcommand{\cvitemtitle}[2]{\textbf{\textcolor{textmain}{#1}}\cvdate{#2}}
\newcommand{\cvsubline}[1]{\textcolor{muted}{#1}}
\newcommand{\smallgap}{\vspace{2pt}}

% =========================
\begin{document}
\color{textmain}

% =========================
% Header
% =========================
\begin{tabularx}{\textwidth}{X r}
{\Huge \textbf{Minseong Cho}} &
\begin{minipage}[t]{0.43\textwidth}\raggedleft
\faEnvelope\ \href{mailto:mscho713@ajou.ac.kr}{mscho713@ajou.ac.kr}\\
\faPhone\ \href{tel:+821088037786}{+82 10-8803-7786}\\
\faGlobe\ \href{https://aloha713.github.io}{aloha713.github.io}\\
\faGraduationCap\ \href{https://scholar.google.com/citations?user=j9RODW0AAAAJ}{Google Scholar}\\
\textcolor{muted}{Suwon, South Korea}
\end{minipage}
\end{tabularx}

\vspace{6pt}
\textcolor{muted}{M.S. student in Mechanical Engineering, Ajou University \sep Active matter \sep Leidenfrost dynamics \sep Hair frizz dynamics}

% =========================
\section*{Summary}
Currently a graduate researcher at Ajou University. My research interests include active matter dynamics, the Leidenfrost effect, and hair frizz dynamics.

% =========================
\section*{Research Interests}
Active matter dynamics; Leidenfrost-induced motion; soft matter and fluid--structure interaction; hair frizz dynamics; centerline curvature and excursion analysis.

% =========================
\section*{Education}
\begin{itemize}
  \item \cvitemtitle{M.S. in Mechanical Engineering}{Sep 2025 -- Present}\\
  \href{https://www.ajou.ac.kr/en/index.do}{Ajou University}, Suwon, South Korea
  \begin{itemize}
    \item \cvfield{Advisor}{Prof. Jonghyun Ha}
  \end{itemize}

  \item \cvitemtitle{B.S. in Mechanical Engineering}{Mar 2020 -- Aug 2025}\\
  \href{https://www.ajou.ac.kr/en/index.do}{Ajou University}, Suwon, South Korea
\end{itemize}

% =========================
\section*{Research Experience}
\begin{itemize}
  \item \cvitemtitle{Graduate Research Student}{Sep 2025 -- Present}\\
  \href{https://www.softlab.ajou.ac.kr/}{Softlab}, Ajou University
  \begin{itemize}
    \item \cvfield{Topics}{Hair frizz dynamics; boundary-driven active matter in soft hydrogels}
    \item Study hair frizz dynamics using centerline-based geometric analysis and simulation-assisted interpretation.
    \item Analyze boundary-driven active matter in soft hydrogels, focusing on Leidenfrost-induced dynamics.
    \item Develop reproducible analysis and visualization scripts for experimental and simulation data.
    \item \cvfield{Advisor}{Prof. Jonghyun Ha; Dr. Yeonsu Jung}
  \end{itemize}

  \item \cvitemtitle{Undergraduate Research Student}{Mar 2023 -- Aug 2025}\\
  \href{https://www.softlab.ajou.ac.kr/}{Softlab}, Ajou University
  \begin{itemize}
    \item \cvfield{Topics}{Boundary-driven active matter in soft hydrogels}
    \item Conducted research on Leidenfrost-related soft-matter dynamics.
    \item Performed image-based tracking, quantitative analysis, and figure preparation for presentations.
    \item \cvfield{Advisor}{Prof. Jonghyun Ha; Dr. Yeonsu Jung}
  \end{itemize}
\end{itemize}

% =========================
\section*{Selected Presentations}
\begin{itemize}
  \item \cvitemtitle{APS Division of Fluid Dynamics Meeting}{Nov 2025}\\
  \cvorg{Houston, TX, USA}
  \begin{itemize}
    \item \textit{Leidenfrost-induced active matter dynamics of spherical hydrogels}
  \end{itemize}

  \item \cvitemtitle{Asian Congress of Fluid Mechanics}{Sep 2025}\\
  \cvorg{Seoul, South Korea}
  \begin{itemize}
    \item \textit{Leidenfrost-induced active matter dynamics of spherical hydrogels}
  \end{itemize}

  \item \cvitemtitle{KSME Annual Conference}{Nov 2024}\\
  \cvorg{Jeju, South Korea}
  \begin{itemize}
    \item \textit{Explosive motion of spherical hydrogel via the Leidenfrost effect}
  \end{itemize}
\end{itemize}

% =========================
\section*{Awards \& Honors}
\begin{itemize}
  \item \cvitemtitle{Dean's List}{Spring 2024, Spring 2025}\\
  \cvorg{Ajou University}
  \begin{itemize}
    \item Recognized for outstanding academic performance (top 5\% of the department).
  \end{itemize}

  \item \cvitemtitle{Capstone Design Competition}{June 2025}\\
  \cvorg{Ajou University}
  \begin{itemize}
    \item \cvaward{2nd Place; KRW 1,000,000 prize}
    \item \cvfield{Project}{Compliant-mechanism-based knee assistive device for degenerative osteoarthritis prevention}
  \end{itemize}

  \item \cvitemtitle{Gyeonggi-do Assistive Device Idea Competition}{Nov 2025}\\
  \cvorg{Gyeonggi Province Rehabilitation Engineering Service Support Center (South Korea)}
  \begin{itemize}
    \item \cvaward{3rd Place; KRW 300,000 prize}
    \item \cvfield{Project}{Compliant-mechanism-based knee assistive device for older adults}
  \end{itemize}

  \item \cvitemtitle{APS DFD Travel/Enabling Grant}{2025}\\
  \cvorg{APS Division of Fluid Dynamics, American Physical Society}
  \begin{itemize}
    \item \cvaward{US\$750 travel cost reimbursement}
    \item Travel support for participation in the APS Division of Fluid Dynamics Meeting.
  \end{itemize}

  \item \cvitemtitle{Gallery of Fluid Motion}{Apr 2026}\\
  \cvorg{The Korean Society of Mechanical Engineers, Fluid Engineering Division}
  \begin{itemize}
    \item \cvaward{Haecheon Choi GFM Award; KRW 400,000 prize}
    \item \cvfield{Title}{Explosive motion of spherical hydrogel via the Leidenfrost effect}
    \item \cvfield{Authors}{Minseong Cho, Yeonsu Jung, Jonghyun Ha}
  \end{itemize}
\end{itemize}

% =========================
\section*{Selected Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Programming} & Python, MATLAB, LaTeX \\
\textbf{Tools} & DeepLabCut, OpenCV, Git, Overleaf \\
\textbf{Methods} & image-based tracking, trajectory analysis, centerline extraction, curvature/excursion profiling, data visualization \\
\end{tabularx}

% =========================
\section*{References}
\textbf{Prof. Jonghyun Ha}\\
\textit{Assistant Professor, Department of Mechanical Engineering, Ajou University, Suwon, South Korea}\\
E-mail: \href{mailto:hajh@ajou.ac.kr}{hajh@ajou.ac.kr}\\
Scholar Profiles:
\href{https://www.softlab.ajou.ac.kr/people-ha}{Personal Page} \sep
\href{https://scholar.google.com/citations?user=H73RmsAAAAAJ}{Google Scholar}\\[5pt]

\textbf{Dr. Yeonsu Jung}\\
\textit{Postdoctoral Research Fellow, School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, USA}\\
E-mail: \href{mailto:jung@seas.harvard.edu}{jung@seas.harvard.edu}\\
Scholar Profiles:
\href{https://yeonsu-jung.github.io}{Personal Page} \sep
\href{https://scholar.google.com/citations?user=BMZc1CcAAAAJ}{Google Scholar}

\end{document}
